---
title: "model-performance-linear"
author: "Murugesan Nagarajan"
date: "4/16/2018"
output: html_document
---

```{r eval=TRUE}
raw_data <- read.csv('/Projects/R/CSX415-project/phone_mark/data/bank.csv',sep=';')
ind <- sample(2,nrow(raw_data), replace = TRUE, prob = c(0.8,0.2))
train_data <- raw_data[ind==1,]
test_data <- raw_data[ind==2,]

glmmodel <- glm(y~ age + job + marital + education + default + balance + housing + loan + contact + duration + campaign + pdays + previous + poutcome, data = train_data,family=binomial)
print(glmmodel)

```

Plot the model

```{r eval=TRUE}
plot(glmmodel)
```


To test the hypothesis H0: B1=B2=0, We can compare our model with a reduced model that only contains an intercept term. A likelihood ratio test comparing the full and reduced models can be performed using the anova() function.

```{r eval=TRUE}
reduced=glm(y~1,data=train_data,family=binomial)
anova(reduced,glmmodel,test="Chisq")
```

As a next step, lets perform tests on the individual regression parameters

```{r eval=TRUE}
summary(glmmodel)
```

To create a 95% confidence interval for the estimate,
```{r eval=TRUE}
exp(confint.default(glmmodel))
```

To predict the probability that a customer will sign up for a term deposit.

```{r eval=TRUE}
predict_glm=predict.glm(glmmodel,test_data,type="response",se.fit=TRUE)

```
predict_glm$fit

# Performance evaluation

```{r eval=TRUE}
pred=predict(glmmodel,newdata=test_data)
accuracy <- table(pred,test_data$y)
sum(diag(accuracy))/sum(accuracy)

```
# Conclusion

The accuracy of the model is very less when we use this glm model.  Need to do further analysis on this data.



