---
title: "performance"
author: "Murugesan Nagarajan"
date: "5/8/2018"
output:
  pdf_document: default
  html_document: default
---
## Analysis

The dataset contains 20 features which are used to predict the target. Our aim is to predict whether a customer with these features will subscribe for a Banking product. The data set is ';' separated data set and we can directly read and use it for our analysis. Caret package will be used for this model development and performance evaluation. We will try to build GBM, Random Forest, Neural Network and Logistic regression from the caret package and then we will display the performance metrics.

The below code will read the data from the CSV file and create an R data frame objects.

```{r eval=TRUE}
library("caret")
print(getwd())
raw_data <- read.csv('/Projects/R/CSX415-project/phone_mark/data/bank.csv',sep=';')

```

## Attribute Information

The dataset has the below features and we need to identify the feature importance and then need to use those features for classification.

### Input variables:

```{r eval=FALSE}

#bank client data:
1 - age (numeric)
2 - job : type of job (categorical: 'admin.','blue-collar','entrepreneur','housemaid','management','retired','self-employed','services','student','technician','unemployed','unknown')
3 - marital : marital status (categorical: 'divorced','married','single','unknown'; note: 'divorced' means divorced or widowed)
4 - education (categorical: 'basic.4y','basic.6y','basic.9y','high.school','illiterate','professional.course','university.degree','unknown')
5 - default: has credit in default? (categorical: 'no','yes','unknown')
6 - housing: has housing loan? (categorical: 'no','yes','unknown')
7 - loan: has personal loan? (categorical: 'no','yes','unknown')
#related with the last contact of the current campaign:
8 - contact: contact communication type (categorical: 'cellular','telephone') 
9 - month: last contact month of year (categorical: 'jan', 'feb', 'mar', ..., 'nov', 'dec')
10 - day_of_week: last contact day of the week (categorical: 'mon','tue','wed','thu','fri')
11 - duration: last contact duration, in seconds (numeric). Important note: this attribute highly affects the output target (e.g., if duration=0 then y='no'). Yet, the duration is not known before a call is performed. Also, after the end of the call y is obviously known. Thus, this input should only be included for benchmark purposes and should be discarded if the intention is to have a realistic predictive model.
#other attributes:
12 - campaign: number of contacts performed during this campaign and for this client (numeric, includes last contact)
13 - pdays: number of days that passed by after the client was last contacted from a previous campaign (numeric; 999 means client was not previously contacted)
14 - previous: number of contacts performed before this campaign and for this client (numeric)
15 - poutcome: outcome of the previous marketing campaign (categorical: 'failure','nonexistent','success')
#social and economic context attributes
16 - emp.var.rate: employment variation rate - quarterly indicator (numeric)
17 - cons.price.idx: consumer price index - monthly indicator (numeric) 
18 - cons.conf.idx: consumer confidence index - monthly indicator (numeric) 
19 - euribor3m: euribor 3 month rate - daily indicator (numeric)
20 - nr.employed: number of employees - quarterly indicator (numeric)

### Output variable (desired target):
21 - y - has the client subscribed a term deposit? (binary: 'yes','no')

```




## Data cleaning
checks if inout dataset contains any empty values for any of the features.
```{r eval=TRUE}

sum(is.na(raw_data))

```

The dataset does not have any empty value since the above function returned the empty count as 0

## Data split

Use the caret function to divide the data into two set 75% of data as training set and 25% of data as testset

```{r eval=TRUE}
index<-createDataPartition(raw_data$y,p=0.5,list=FALSE)
trainset<- raw_data[index,]
testset<-raw_data[-index,]
outcomeName<-'y'

```

Plot the target variable as a histogram chart and find what percentage of the data is yes and what percentage of data is No. It seems we have less than 20% of data is having the target as Yes and more than 80% of the data are having the target as No. It looks like only small no if customer signed for the banking product as per this dataset.

```{r eval=TRUE}
histogram(trainset$y)
```

## Feature selection using caret

Instead of using all the features, Lets try to find the important features that are corelated with the target and use those top 5 features for our prediction.

```{r eval=FALSE}
control <- rfeControl(functions = rfFuncs,method = "repeatedcv",repeats = 3,verbose = FALSE)
predictors<-names(trainset)[!names(trainset) %in% outcomeName]
Loan_Pred_Profile <- rfe(trainset[,predictors], trainset[,outcomeName],rfeControl = control)

```
consider only the top 5 features as per the above feature selection and draw the historgram for all these features to look at the distribution.

```{r eval=TRUE}
predictors<-c("duration", "month", "poutcome", "pdays", "previous")

histogram(trainset$duration)

histogram(trainset$month)
histogram(trainset$poutcome)

histogram(trainset$pdays)
histogram(trainset$previous)

```

## Training the model
Apply GBM, Random forest, Neural Net and Logistic Regression using the caret package train function.

```{r eval=FALSE}
model_gbm<-train(trainset[,predictors],trainset[,outcomeName],method='gbm')
model_rf<-train(trainset[,predictors],trainset[,outcomeName],method='rf')
model_nnet<-train(trainset[,predictors],trainset[,outcomeName],method='nnet')
model_glm<-train(trainset[,predictors],trainset[,outcomeName],method='glm')
```

## Prediction
Predict the outcome of test data and then evaluate the model performance

Evaluate the random forest model using the metrics
--------------------------------------------------

```{r eval=FALSE}
predict<-predict.train(object=model_rf,testset[,predictors],type="raw")
table(predict)
confusionMatrix(predict,testset[,outcomeName])
```
## Model performance for Random Forest

confusion matric for the Random Forest model

Prediction|no|yes
----------|----|----
No|1927|161
Yes|73|99



evaluate the GBM model and find the metrics
--------------------------------------------

```{r eval=FALSE}
predict<-predict.train(object=model_gbm,testset[,predictors],type="raw")
table(predict)
confusionMatrix(predict,testset[,outcomeName])
```
## Model performance for GBM

confusion matric for the GBM model

Prediction|no|yes
----------|---|----
No|1954|189
Yes|46|71

evaluate the Neural Net model and calculate the metrics.
---------------------------------------------------------
```{r eval=FALSE}
predict<-predict.train(object=model_nnet,testset[,predictors],type="raw")
table(predict)
confusionMatrix(predict,testset[,outcomeName])
```
## Model performance for Neural Networks

confusion matric for the Neural Networks

Prediction|no|yes
----------|---|---
No|1930|147
Yes|70|113



evaluate the glm and calculate the metrics.
-------------------------------------------
```{r eval=FALSE}
predict<-predict.train(object=model_glm,testset[,predictors],type="raw")
confusionMatrix(predict,testset[,outcomeName])
```
## Model performance for Logistic Regression

confusion matric for the Logistic Regression

Prediction|no|yes
----------|---|----
No|1962|179
Yes|38|81

## Conclusion

Calculated the performance metrics, accuracy, Sensitivity,Specificity, and Kappa. As per these metrics, We can either use Random Forest or Neural Network model for this classification problem and predict better target.

|Model|Accuracy|Sensitivity|Specificity|Kappa|
|:-----|:--------|:--------------|:-----------------------|------------|
|GBM|90|97|31|37|
|Random Forest|90|97|33|39|
|Neural Network|90|96|37|41|
|Logistic Regression|89|97|28|35|
